---
title: "101_WK4_Data_Vis_Basic"
author: "Seung Hyun Sung"
date: "11/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# ANATOMY OF A GGPLOT2 OBJECT ----


## 1A Framing ggplot 
Think of ggplots like building layers of a cake. Each layer is added on top.

[1] Create a canvas defined by mapping to columns in your data 

[2] Add 1 or more geometrics (geoms)

[3] Add formatting features. {Scales, Themes, Facets, etc}

Geom/Geometries: These define how your data looks on your plot 

* Stands for geometrics
* Geometrics are the funcdermental way to represent data in your plot
* Determines Plot Type:
 + Histograms
 + Scatter Plots
 + Box Plots
 + Bar/Column Plots
 + More and more 

Formatting: These add customization to your plot to control wide-range of appearence options. 
Scales, Faceting, Position Adjustments, Labels, Legends, Themes are commonly customerized. 


```{r, include =FALSE}
library(tidyverse)
library(lubridate)
library(tidyquant)
```


>_Enables Customization on Steroids
ggplot2 is super flexible giving tons of options. The downside in this flexibility is that it takes a while to learn._ _Matt Dancho_
----

>_For business reports the it is important to get the themes right and reported with same formated theme._ __ _Matt Dancho_

>_The key to a good ggplot is knowing how to format the data for a ggplot._ 


```{r, include =FALSE}
getwd()
bike_orderlines_tbl <- read_rds("00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


## 1B How ggplot works ----

### Step 1: Format data ----

unlike base graphics, ggplot works with data.frames and not individual vectors. 

    
```{r}

revenue_by_year_tbl <- bike_orderlines_tbl %>%
    select(order_date, total_price) %>%
    mutate(year = year(order_date)) %>%
    
    group_by(year) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup()


revenue_by_year_tbl

```


### Step 2: Plot ----

Mapping: Connects data columns to ggplot aesthetics 

GGplot structure 

+ Step 1: Build Canvas: Involves mapping __columns__ in data to ggplot() __aesthetics__ (x, y, color, fill, size etc) via aes() function 

+ Step 2: Geometries: 2nd Layer that generates a visual depiction of the data using a geometry type (e.g. Line Plot)

```{r}
revenue_by_year_tbl %>%
    # Canvas
    ggplot(aes(x = year, y = revenue, color = revenue)) +
    
    # Geometries 
    geom_line(size = 1) +
    # aesthetics specifically targeting certain geometries 
    geom_point(aes(size = revenue))
```


+ Scale Color: Enables customizing the color aesthetic (mapped to revenue in this case)

+ Scale X & Y: Enables customizing the x-axis and y-axis (mapped to year and revenue in this case)

+ Labels: Changes the __text__ for title, subtitle, x, y, legends & captions 

+ Themes: Usually we start with a base theme e.g. theme_bw() and then modify with the theme() function  

```{r}
g <- revenue_by_year_tbl %>%
    # Canvas
    ggplot(aes(x = year, y = revenue, color = revenue)) +
    
    # Geometries 
    geom_line(size = 1) +
    geom_point(size = 5) +
    geom_smooth(method = "lm", se = FALSE) +
    
    # Formatting
    expand_limits(y = 0) +
    scale_color_continuous(low = "red", high = "black",
                           labels = scales::dollar_format(scale = 1/1e6, suffix = "M")) +
    scale_y_continuous(labels = scales::dollar_format(scale = 1/1e6, suffix = "M")) +
    labs(
        title = "Revenue",
        subtitle = "Sales are trending up and to the right!",
        x = "",
        y = "Sales (Millions)",
        color = "Rev ($M)",
        caption = "What's happening?\nSales numbers showing year-over-year growth."
    ) +
    theme_bw() +
    theme(legend.position = "right", legend.direction = "vertical")
```

## 1C What is a ggplot? ----

Key Concept: The ggplot object is just a list that captures layers, scales, 
mappings, theme, coordinates, and labels that you customize

```{r}
g

```


# Types of Graphs: ggplot2 Geometries 

```{r}
bike_orderlines_tbl <- read_rds("00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


## 2A Point / Scatter Plots (geom_point)

* Great for Continuous vs Continuous

* Also good for Lollipop Charts (more on this in advanced plots)

Goal: Explain relationship between order value and quantity of bikes sold

```{r}
# Data Manipulation
order_value_tbl <- bike_orderlines_tbl %>% 
    select(order_id, order_line, total_price, quantity) %>% 
    group_by(order_id) %>% 
    summarise(
        total_quantity = sum(quantity),
        total_price    = sum(total_price)
    ) %>% 
    ungroup()
    
    
# Scatter Plot
order_value_tbl %>% 
    ggplot(aes(x = total_quantity, y = total_price)) +
    # geometries
    geom_point(alpha = 0.5, size = 2) +
    # uses spine (default) y ~ s(x, bs = "cs")
    # change method to 'lm'
    geom_smooth(method = 'lm', se = FALSE)
```



## 2B Line Plots ----

* Great for time series

* Goal: Describe revenue by Month, expose cyclic nature

```{r}
# Data Manipulation
revenue_by_month_tbl <- bike_orderlines_tbl %>% 
    select(order_date, total_price) %>% 
    mutate(year_month = floor_date(order_date, "months") %>% ymd()) %>% 
    group_by(year_month) %>% 
    summarise(revenue = sum(total_price)) %>% 
    ungroup()
    
    

# Line Plot
revenue_by_month_tbl %>% 
    ggplot(aes(x = year_month, y = revenue)) + 
    geom_line(size = 0.5, linetype = 1) +
    geom_smooth(method = 'loess', span = 0.2)

```

## 2C Bar / Column Plots ----

* - Great for categories

* Goal: Sales by Descriptive Category

```{r}
# Data Manipulation
revenue_by_category_2 <- bike_orderlines_tbl %>% 
    select(category_2, total_price) %>% 
    group_by(category_2) %>% 
    summarise(revenue = sum(total_price)) %>% 
    ungroup()


# Bar Plot
revenue_by_category_2 %>% 
    mutate(category_2 = category_2 %>% fct_reorder(revenue)) %>% 
    ggplot(aes(x = category_2, y = revenue)) +
    geom_col(fill = palette_dark()[6]) +
    coord_flip()
```

***
#### R - difference between geom_bar() and geom_col() in ggplot2

* There are two types of bar charts: geom_bar() and geom_col(). 

* geom_bar() makes the height of the bar proportional to the number of cases in each group (or if the weight aesthetic is supplied, the sum of the weights). If you want the heights of the bars to represent values in the data, use geom_col() instead
geom_bar() uses stat_count() by default: it counts the number of cases at each
x position

* summary:
    + geom_bar : represents stats (number of cases in each group)
    + geom_bar : represents value


## 2D Histogram / Density Plots ----

* Great for inspecting the distribution of a variable


* Goal: Unit price of bicycles


```{r}
# Histogram
bike_orderlines_tbl %>% 
    distinct(model, price) %>% 
    ggplot(aes(price)) +
    geom_histogram(bins = 20, color = "white", fill = "blue", alpha = 0.5) 

# Goal: Unit price of bicylce, segmenting by frame material

# Histogram
bike_orderlines_tbl %>% 
    distinct(model, price, frame_material) %>% 
    ggplot(aes(price, fill = frame_material)) +
    geom_histogram() +
    facet_wrap(~frame_material, ncol = 1) +
    scale_fill_tq() +
    theme_tq()

# Density
bike_orderlines_tbl %>% 
    distinct(model, price, frame_material) %>% 
    ggplot(aes(price, fill = frame_material)) +
    geom_density(alpha = 0.5) +
    scale_fill_tq() +
    theme_tq()

```




##  2E Box Plot / Violin Plot ----

* Great for comparing distributions

* Goal: Unit price of models, segmenting by category 2

```{r}
# Data Manipulation
unit_price_by_cat_2_tbl <- bike_orderlines_tbl %>% 
    select(category_2, model, price) %>% 
    distinct() %>% 
    mutate(category_2 = as_factor(category_2) %>% fct_reorder(price))

# Box Plot
unit_price_by_cat_2_tbl %>% 
    ggplot(aes(category_2, price)) +
    geom_boxplot() +
    coord_flip() +
    theme_tq()
```



#  2F Violin Plot & Jitter Plot

* It adds a small amount of random variation to the location of each point, and is a useful way of handling overplotting caused by discreteness in smaller datasets.

```{r}
unit_price_by_cat_2_tbl %>% 
    ggplot(aes(category_2, price)) +
    geom_jitter(width = 0.1, color = "#2c3e50") +
    geom_violin(alpha = 0.5) +
    coord_flip() +
    theme_tq()
```



# 2G Adding Text & Labels ----

* Goal: Exposing sales over time, highlighting outlier

```{r}
# Data Manipulation
revenue_by_year_tbl <- bike_orderlines_tbl %>% 
    select(order_date, total_price) %>% 
    mutate(year = year(order_date)) %>% 
    group_by(year) %>% 
    summarise(revenue = sum(total_price)) %>% 
    ungroup()
```


#### Adding text to bar chart
```{r}
revenue_by_year_tbl %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill="#2c3e50") +
    geom_text(aes(label = scales::dollar(revenue, scale = 1e-6, suffix = "M")), vjust = 1.5, color = "white") 

revenue_by_year_tbl %>% 
    mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill="#2c3e50") +
    geom_text(aes(label = revenue_text), vjust = 1.5, color = "white") +
    expand_limits(y = 2e7) +
    theme_tq()
```


```{r}
revenue_by_year_tbl %>% 
    mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill="#2c3e50") +
    geom_label(aes(label = revenue_text), vjust = 0.6, size = 5) +
    expand_limits(y = 2e7) +
    theme_tq()

revenue_by_year_tbl %>% 
    mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill="#2c3e50") +
    geom_label(aes(label = revenue_text), vjust = 0.05, size = 5) +
    expand_limits(y = 2e7) +
    theme_tq()
```


#### Filtering labels to highlight a point
```{r}
revenue_by_year_tbl %>% 
    mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill="#2c3e50") +
    geom_smooth(method = "lm", se = FALSE) +
    geom_text(aes(label = revenue_text), vjust = 1.5, color = "white") +
    geom_label(label = "Major Demand This Year",
               vjust = -0.5,
               size = 5, 
               fontface = "bold",
               fill = palette_light()[4],
               data = revenue_by_year_tbl %>% 
                   filter(year %in% c(2013))) +
    expand_limits(y = 2e7) +
    theme_tq()
```


# 3.0 ggplot2 Formatting 


# 3A. Data Manipulation

fct_reorder  : reorder by one axis (e.g. revenue)

fct_reorder2 : reorder by two axis (e.g. year, revenue)


```{r, message=FALSE}
sales_by_year_category_2_tbl <- bike_orderlines_tbl %>%
    select(order_date, category_2, total_price) %>%
    
    mutate(order_date = ymd(order_date)) %>%
    mutate(year = year(order_date)) %>%
    
    group_by(category_2, year) %>%
    summarize(revenue = sum(total_price)) %>%
    ungroup() %>%
    
    mutate(category_2 = fct_reorder2(category_2, year, revenue))

sales_by_year_category_2_tbl
```

```{r}
sales_by_year_category_2_tbl %>% 
    mutate(category_2_num = as.numeric(category_2)) %>% 
    arrange(category_2_num)

```

## 3B working with colors 

It is important to be comfrontable working with colors 

### 3B.1 Color Conversion 


```{r}
colours()

sales_by_year_category_2_tbl %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill = "slateblue2")
```

#### To RGB : Specifying color values as combinations of Red - Green - Blue 
(e.g. White = 255 - 255 - 255)

```{r}
col2rgb("slateblue2")

col2rgb("#2C3E50")
```

#### To Hex : Specifying a color by hexidecimal 

```{r}
rgb(44, 62, 80, maxColorValue = 225)
```



### 3B.2 Color Paletters 

tidyquant 
```{r}
tidyquant::palette_light()[1] %>% col2rgb()
```

Brewer : for discrete data 
```{r}
RColorBrewer::display.brewer.all()
RColorBrewer::brewer.pal.info %>% arrange(desc(maxcolors))
RColorBrewer::brewer.pal(n = 100, name = "Blues")  

sales_by_year_category_2_tbl %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill = RColorBrewer::brewer.pal(n = 100, name = "Blues")[3])
```


Viridis : 
```{r}

viridisLite::viridis(n = 20)

sales_by_year_category_2_tbl %>% 
    ggplot(aes(x = year, y = revenue)) +
    geom_col(fill = viridisLite::viridis(n = 20)[5])
```

# 4.0 Aesthetic Mappings 

## 4B color 
Used with line nd points, Outlines of rectangular objects 

ggplot2 data format & Modeling data format are the same! 

"Tidy Data": One column of interest known as the target (e.g. target = revenue)

Other columns describe the target 
```{r}
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, color = category_2)) + # define Globally 
    geom_line() +
    geom_point()

sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue)) +
    geom_line(aes(color = category_2)) +  # Define locally 
    geom_point()

sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue)) +
    geom_line(aes(color = category_2)) +
    geom_point(color = "dodgerblue", size = 2)
```

## 4B Fill

Info: 
* Used with fill of rectangular objects

* Do not confuse with colour and fill argument 

```{r}
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue)) + # define Globally 
    geom_col() 

sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, fill = category_2)) + # define Globally 
    geom_col() 

# Do not confuse fill with colour!!! 
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, color = category_2)) + # define Globally 
    geom_col() 
```


## 4B Size

Info :

* Used with points 
```{r}
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue)) +
    geom_line(aes(colour = category_2), size = 1) +
    geom_point(aes(size = revenue))

sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, size = revenue)) +
    geom_line(aes(colour = category_2)) +
    geom_point()

sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, size = revenue)) +
    geom_line(aes(colour = category_2), size = 1) +
    geom_point()
```

# 5.0 Faceting ---

Great way to tease out variation by category 

Goal: Sales annual sales by category 2 

```{r}
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, colour = category_2)) +
    geom_line(colour = "black") +
    geom_smooth(method = "lm", se = FALSE) +
    facet_wrap(~ category_2, ncol = 3, scales = "free_y") +
    expand_limits(y = 0) 

```

# 6.0 Position Adjustments (Stack & Dodge)

* Stacked Bars & Side-By-Side Bars
    + position = "Stack": Stack elements on top of each other 
    + position_dodge(): Enables further customization of width and height attributes
    
```{r}
# Stacked Bars & Side-By-Side Bars
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, fill = category_2)) +
    # geom_col(position = "stack") +
    # geom_col(position = "dodge") +
    geom_col(position = position_dodge(width = 0.9), color = "white")

# Stacked Area
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, fill = category_2)) +
    geom_area(colour = "black")

```

# 7.0 Scales (colours, Fills. Axis)

* continuous (e.g. Revenue): Changes color via gradient palette
* Categorical (e.g.): Changes colour via discrete palette

Plot 1: Faceted Plot, Colour = Continous Scale 
```{r}

g_facet_continous <- sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, colour =revenue)) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    
    facet_wrap(~ category_2, scales = "free_y") +
    expand_limits(y = 0) +
    theme_minimal()

g_facet_continous
```
Plot 2: Faceted Plot, Colour = Discrete Scale
```{r}
g_facet_discrete <- sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, colour = category_2)) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    facet_wrap(~category_2, scales = "free_y") +
    expand_limits(y = 0)

g_facet_discrete
```

Plot 2: Stacked Area plot
```{r}
g_area_discrete <- sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, fill = category_2)) +
    geom_area(colour = "black") +
    theme_minimal()

g_area_discrete
```


## 7.2 Scale Colours & Fills

- Awesome way to show variation by groups (discrete) and by values (continuous)
- Because we have colour = category_2 

colour by Revenue (continuous Scale): adjusting colour gradient 
```{r}
g_facet_continous +
    scale_color_continuous(
        low  = "cornflowerblue",
        high = "black" 
    )

g_facet_continous +
    scale_color_viridis_c(alpha = 0.7)

```

colour by Category 2: __discrete__ Scale

```{r}
g_facet_discrete +
    scale_color_viridis_d()

g_facet_discrete +
    scale_color_brewer(palette = "PuRd") +
    theme_dark()

# RColorBrewer::display.brewer.all()
```

Fill by Category 2

```{r}
RColorBrewer::display.brewer.all()

g_area_discrete +
    scale_fill_brewer(palette = "Set3")

g_area_discrete +
    scale_fill_viridis_d()

g_area_discrete +
    scale_fill_tq() 
```

## 7.3 Axis Scales 

```{r}
g_facet_continous +
    scale_color_viridis_c(alpha = 0.8) +
    # gives more room to breath on the x-axis 
    scale_x_continuous(breaks = seq(2011, 2015, by = 2)) +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M")) +
    theme_minimal()
```

# 8.0 Labels 

```{r}
g_facet_continous +
    scale_x_continuous(breaks = seq(2011, 2015, by = 2)) +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M")) +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
    
    scale_color_viridis_c() +
    theme_dark() +
    
    labs(
        title = "Bike Sales",
        subtitle = "Sales are trending up",
        caption = "5 year sales trends\ncomes from our RP Data base",
        x = "Year",
        y = "Revenue ($M)",
        colour = "Revenue"
    )
    
```


# 9.0 Labels 

theme_light(): Pre-set theme
theme(): The function used to adjust every theme element that is part of a ggplot object 
```{r}
g_facet_continous +
    theme_light() +
    theme(
        axis.text.x = element_text(
            angle = 45, 
            hjust = 1
            ),
        strip.background = element_rect(
            colour = "black", 
            fill   = "cornflowerblue",
            size   = 1
            ),
        strip.text = element_text(
            face = "bold",
            colour = "White"
        )
    )

```

10.0 Putting it All Together 

```{r}
sales_by_year_category_2_tbl %>% 
    ggplot(aes(year, revenue, fill = category_2)) +
    geom_area(colour = "white") +
    
    scale_fill_brewer("Blues", direction = -1) +
    scale_y_continuous(label = scales::dollar_format(scale = 10e-6, suffix = "M")) +
    
    labs(
        title = "Sales Over Year by Category 2",
        subtitle = "Sales Trending Up",
        caption = "Bike Sales trends look strong heading into 2016",
        x = "",
        y = "Revenue ($M)",
        fill = "2nd Category"
    ) +
    theme_minimal() +
    theme(
        title = element_text(face = "bold", colour = "#08306B")
    )

```






