---
title: "101_wk4_Adv_Vis"
author: "Seung Hyun Sung"
date: "11/10/2021"
output:
  pdf_document: default
  html_document: default
---

# DS4B 101-R: R FOR BUSINESS ANALYSIS ---- 
# ADVANCED BUSINESS PLOTS ----

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(tidyverse)
library(lubridate)
library(tidyquant)
library(formattable)

options(digits = 2, scipen = 99)

bike_orderlines_tbl <- read_rds("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```


## 1.0 Lollipop Chart: Top N Customers 

* - Great for showing order

Question: How much purchasing power is in top 5 customers?
Goal: Visualize top N customers in terms of Revenue, include cumulative percentage



### Data Manipulation

```{r}
n <- 10

top_customers_table <- bike_orderlines_tbl %>% 
    select(bikeshop_name, total_price) %>% 
    mutate(bikeshop_name = as_factor(bikeshop_name) %>% fct_lump(n = n, w = total_price)) %>% 
    group_by(bikeshop_name) %>% 
    summarise(revenue = sum(total_price)) %>% ungroup() %>% 
    mutate(bikeshop_name = bikeshop_name %>% fct_reorder(revenue)) %>% 
    mutate(bikeshop_name = bikeshop_name %>% fct_relevel("Other", after = 0)) %>% 
    arrange(desc(bikeshop_name)) %>% 
    
    # Revenue Text
    mutate(revenue_text = scales::dollar(revenue, scale = 1e-6, suffix = "M")) %>% 
    
    # Cumulative Percent 
    mutate(cum_pct = cumsum(revenue)/sum(revenue)) %>% 
    mutate(cum_pct_text = scales::percent(cum_pct)) %>% 
    
    # Rank 
    mutate(rank = row_number()) %>% 
    # NA_integer_: NA Values must match the data type. The NA_integer_ adds an NA value to integer data. 
    mutate(rank = case_when(
        rank == max(rank) ~ NA_integer_,
        TRUE ~ rank
        )) %>% 
    
    #Label Text 
    mutate(label_text = str_glue("Rank: {rank}\nRev: {revenue_text}\nCumPct: {cum_pct_text}"))
    

top_customers_table
```
### Data Visualization

```{r}
top_customers_table %>% 
    # Geometrics
    ggplot(aes(revenue, bikeshop_name)) +
    geom_segment(aes(xend = 0, yend = bikeshop_name), size = 0.5) +
    geom_point(aes(size = revenue)) +
    
    # Label 
    geom_label(aes(label = label_text), 
               size = 1.5, 
               hjust = "inward",
               colour = palette_light()[1]) +
    
    # Formatting
    scale_x_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M")) +
    labs(
        title = str_glue("top {n} Customers"),
        subtitle = str_glue("Start: {min(bike_orderlines_tbl$order_date)}
                             End:  {max(bike_orderlines_tbl$order_date)}"),
        x = "Revenue",
        y = "Bikeshop",
        caption = str_glue("Top 6 customers contribute 51% of purchasing power.")
    ) +
    theme_tq() +
    theme(
        legend.position = "none",
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "bold.italic")
    )


```

## 2.0 Heatmaps 
* - Great for showing details in 3 dimensions

Question: Do specific customers have a purchasing prefernce?

Goal: Visualize heatmap of proportion of sales by Secondary Product Category

### Data Manipulation

```{r}
pct_sales_by_customer <- bike_orderlines_tbl %>% 
    
    select(bikeshop_name, category_1, category_2, quantity) %>% 
    
    group_by(bikeshop_name, category_1, category_2) %>% 
    summarise(total_qty = sum(quantity)) %>% ungroup() %>% 
    
    group_by(bikeshop_name) %>% 
    mutate(pct = total_qty/sum(total_qty)) %>% ungroup() %>% 
    
    mutate(bikeshop_name = as_factor(bikeshop_name) %>% fct_rev()) %>% 
    mutate(bikeshop_name_num = as.numeric(bikeshop_name))

```

# Data Visualization

```{r}

pct_sales_by_customer %>% 
    ggplot(aes(category_2, bikeshop_name)) +
    geom_tile(aes(fill = pct)) +
    geom_text(aes(label = scales::percent(formattable(pct, digits =2))), size = 3) +
    
    facet_wrap(~category_1, scales = "free_x") +
    # formatting 
    scale_fill_gradient(low = "white", high = palette_light()[1]) +
    labs(
        title = "Heatmap of Purchasing Habits",
        x = "Bike Type (Category 2)",
        y = "Customer",
        caption = str_glue(
        "Customers that prefer Road: 
        Ann Arbor speed, Austin Cruisers, & Indianapolis Velocipedes
        
        Customers that prefer Mountain: 
        Ithaca Mountain Climbers, Pittsburgh Mountain Machines, & Tampa 29ers")
    ) +
    theme_tq() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        plot.title = element_text(face = "bold"),
        plot.caption = element_text(face = "bold.italic")
    )

```

