---
title: "101_wk5_iteration_with_purrr"
author: "Seung Hyun Sung"
date: "11/15/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# DS4B 101-R: R FOR BUSINESS ANALYSIS ----
# ITERATION WITH PURRR ----


```{r, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(tidyquant)
library(lubridate)
library(broom)

bike_orderlines_tbl <- read_rds("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```



# 1.0 PRIMER ON PURRR ----

### Programmatically getting Excel files into R
```{r}
excel_paths_tbl <- fs::dir_info("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_raw/")

paths_chr <- excel_paths_tbl %>% pull(path)
```



### What Not To Do: Don't use for loops
```{r}
excel_list <- list()
for(path in paths_chr){
    excel_list[[path]] <- read_excel(path)
}
excel_list
```


### What to Do: Use map()

purrr::map : designed for iteration 

Super powerful!!

Anonymous function & functional operation 

* anonymous function: An anonymous function is a function that is not stored in a program file, but is associated with a variable whose data type is function_handle . Anonymous functions can accept multiple inputs and return one output.

* In comparison to functional operation, anonymous function is little more customisable and less typing. 

* For anonymous function must remember to place (.) 

```{r}

excel_list_2 <- paths_chr %>% 
    map(read_excel) %>% 
    # naming the each list of the data frame
    setNames(paths_chr)

# Different variance! 

# Method 1. Function specified with function()
paths_chr %>% 
    map(function(x) read_excel(path = x)) %>% 
    setNames(paths_chr)

# Method 2. anonymous function
paths_chr %>% 
    map(~read_excel(.)) %>% 
    setNames(paths_chr)

```


### Reading Excel Sheets
```{r}
excel_sheets("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_raw/bikes.xlsx") %>%
    map(~ read_excel(path = "~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_raw/bikes.xlsx", sheet = .))

```



# 2.0 MAPPING DATA FRAMES ----

## 2.1 Column-wise Map ----

* Map functions apply a function iteractively to each element of a list or vector.

* date frame is actually a list!!

```{r}
# bike_orderlines_tbl %>% as.list()

bike_orderlines_tbl %>% is.list()

bike_orderlines_tbl %>% 
    map(~class(.)[1]) %>% unlist()

bike_orderlines_tbl %>% 
    select(where(is.numeric)) %>% 
    map(~mean(.)) %>% unlist() 
```


## 2.2 Map Variants ----

* map: list 

* map_chr: character vector

* map_dbl: double(numeric) vector

* map_dfc: data frame (column bind)

* map_int: integer vector 

* map_lgl: logical vector

* walk: triggers side effects, returns the input invisibly 

```{r}
# Charcter map 
bike_orderlines_tbl %>% 
    # these are named character vector 
    map_chr(~class(.)[1])

# Data Frame map
bike_orderlines_tbl %>% 
    map_df(~ class(.)[1])

# Data Frame map + gather 
bike_orderlines_tbl %>% 
    map_df(~ class(.)[1]) %>% 
    gather()

# Observation length map 
bike_orderlines_tbl %>% 
    map_df(~length(.)) %>% 
    gather(key = variable, value = length)

# mean value map 
bike_orderlines_tbl %>% 
    map_df(~mean(.)) %>% 
    gather(key = variable, value = mean)

# NA value map 
bike_orderlines_tbl %>% 
    map_df(~sum(is.na(.))/length(.)) %>% 
    gather(key = variable, value = na)
```



## 2.3 Row-wise Map ----

* keeping excel file organised as tibble 

* This is an alternative way to read all the file from the directory 

* This is the concept of nesting. Very powerful when it is utilised into modelling. Topic of the next section! 

```{r}

excel_tbl <- excel_paths_tbl %>% 
    select(path) %>% 
    mutate(data = path %>% map(read_excel))

excel_tbl
```



# 3.0 NESTED DATA ----

### Unnest

unnest: unnests a nested data frame converting tibbles burried within list-columns to a single level tibble 

* .id = "ID": assign id number with respect to the individual tibbles nested.

* Very important for nesting it back!! 

* Similarly to gather and spread: where mutate row number was a key to return back gather than spread, 
    
```{r}
excel_tbl

excel_tbl$data

# pull second data 
excel_tbl$data[[2]]

# unnests nested data frame 
# brings all the data, expanded the tibbles organised into single data frame
excel_tbl_unnested <- excel_tbl %>% 
    unnest_legacy(data, .id = "ID") 

    
# these data frames originally nested contains different information(features) hence it unnests into single df with all the information preserved. In other words, there will be large amount of NA.
#   %>% View()

```


### Nest
```{r}
excel_tbl_nested <- excel_tbl_unnested %>% 
    group_by(ID, path) %>% 
    nest()
```



### Mapping Nested List Columns

```{r}
# nested excel data 
excel_tbl$data[[1]]

# nested -> unnested -> nested back 
excel_tbl_nested$data[[1]] %>% 
    # select deals with columns: all the columns that 
    # is not all in NA will be droped 
    select_if(~!is.na(.) %>% all())

# Quick example: all() 
# contains 5 NA and 3
x <- c(rep(NA_real_, 5), 3)
is.na(x)
is.na(x) %>% all()

# contains only NA 
y <- rep(NA_real_, 5)
is.na(y)
is.na(y) %>% all()  # Is Y all NA vectors? FALSE 

!is.na(y) %>% all() # Is Y all not NA vectors? TRUE 
```

### Method 1: Creating a function outside of purrr::map()

```{r}
# step 1: create a function that can be mapped to one element 
select_non_na_columns <- function(data){
    data %>%
        select_if(~!is.na(.) %>% all())
}

# step 2: Extract an element, and test the function 
excel_tbl_nested$data[[1]] %>% 
    select_non_na_columns()

# Step 3: Use mutate() + map() 
excel_tbl_nested_fixed <- excel_tbl_nested %>%
    # Remember this nested tibble (tibble inside the tibble) are row operation 
    # Hence the mutate function works beautifully 
    # Here: create new nested set of tibbles (map) 
    mutate(data_fixed = data %>% map(select_non_na_columns))

# Step 4: Check 
excel_tbl_nested_fixed$data_fixed[[1]]
```



# 4.0 MODELING WITH PURRR ----

* Apply modeling functions at scale 

# 4.1 Time Series Plot ----
*  - What if we wanted to approximate the 3 month rolling average with a line?

*  - We can use a smoother

# Code comes from 04_functions_iteration/01_functional_programming
```{r}
rolling_avg_3_tbl <- bike_orderlines_tbl %>%
    select(order_date, category_1, category_2, total_price) %>%
    
    mutate(order_date = ymd(order_date)) %>%
    mutate(month_end = ceiling_date(order_date, unit = "month") - period(1, unit = "days")) %>%
    
    group_by(category_1, category_2, month_end) %>%
    summarise(
        total_price = sum(total_price)
    ) %>%
    mutate(rolling_avg_3 = rollmean(total_price, k = 3, na.pad = TRUE, align = "right")) %>%
    ungroup() %>%
    
    mutate(category_2 = as_factor(category_2) %>% fct_reorder2(month_end, total_price)) 
```

The 3 month moving (rolling) average looks choppy: it was to get the idea of the trend. 

* In statistics, a moving average (rolling average or running average) is a calculation to analyze data points by creating a series of averages of different subsets of the full data set. It is also called a moving mean (MM) or rolling mean and is a type of finite impulse response filter.

* 3 month MA are not centered or aligned + there are missing points: There are down sides.
  + usually align to the right hence does not follow the trend appropriately. 

Often we would like to use smoother other than 3 month rolling average. 


```{r}
rolling_avg_3_tbl %>%
    
    ggplot(aes(month_end, total_price, color = category_2)) +
    
    # Geometries
    geom_point() +
    geom_line(aes(y = rolling_avg_3), color = "blue", linetype = 1) +
    facet_wrap(~ category_2, scales = "free_y") +
    
    # Add Loess Smoother
    # [1] The smoother does not actually follow the trend, must adjust the span argument!  
    # geom_smooth(method = "loess", se = FALSE) +
    geom_smooth(method = "loess", se = FALSE, span = 0.2, colour = "black") +
    
    # Formatting
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar_format(scale = 1e-3, suffix = "K"))
```


# 4.2 Modeling Primer ----

### Data Preparation

```{r}
sales_by_m_cross_country_tbl <- rolling_avg_3_tbl %>% 
  filter(category_2 == "Cross Country Race") %>% 
  
  select(month_end, total_price) %>% 
  # smoother does not work with date data 
  mutate(month_end_num = as.numeric(month_end))

sales_by_m_cross_country_tbl %>% 
  ggplot(aes(x = month_end_num, y = total_price)) +
  geom_point(aes(colour = total_price)) +
  geom_smooth(method = "loess", se = FALSE, span = 0.2)
  
```


### Making a loess model

* Smoothing data using local regression

* Fit a polynomial surface determined by one or more numerical predictors, using local fitting.

```{r}
?loess

fit_loess_cross_country <- sales_by_m_cross_country_tbl %>% 
  # notice here this is not tidy function, the "data" is second argument of loess function
  # hence, you will get error without data = . argument. 
  loess(total_price ~ month_end_num, data = ., span = 0.2)

```



### Working With Broom

* broom has three useful functions stored
  + augment(): retuns model fitted values, residuals, and standard erors in data frame format 
  + tidy() : 
  + glance():
  
```{r}
# we now obtained the smooth data points using loess + broom::augment function 
fit_loess_cross_country %>% 
  # fitted, standard error, residuals from model
  broom::augment() %>% 
  
  # Visualising result 
  ggplot(aes(x = month_end_num, y = total_price)) +
  geom_point() +
  geom_line(aes(y = .fitted))

```

# 4.3 Step 1: Function To Return Fitted Results ----

### Pro Tip: When making functions, save some testable data as each argument so you can interactively test the function while you build it. 

```{r}
# group_by {category_1, category_2} gives 9 total categories 
rolling_avg_3_tbl %>% 
  distinct(category_1, category_2)

rolling_avg_3_tbl_nested <- rolling_avg_3_tbl %>% 
  group_by(category_1, category_2) %>% 
  nest()

rolling_avg_3_tbl_nested$data[[1]]

### Pro Tip: here 
data <- rolling_avg_3_tbl_nested$data[[1]]

tidy_loess <- function(data, span = 0.2){
  
  data_formatted <- data %>% 
    select(month_end, total_price) %>% 
    mutate(month_end_num = as.numeric(month_end))
  
  fit_loess <- loess(formula = total_price ~ month_end_num,
                     data    = data_formatted,
                     span    = 0.2)
  output_tbl <- fit_loess %>% 
    broom::augment() %>% 
    select(.fitted)
  
  return(output_tbl)
}
  
tidy_loess(data)


```

# 4.4 Step 2: Test Function on Single Element ----

```{r}
# test whether the tidy_loess() function operates well with nested tibble 
rolling_avg_3_tbl_nested$data[[6]] %>% 
  tidy_loess()
```



# 4.5 Step 3: Map Function to All Categories ----

### Map Functions
```{r}
loess_tbl_nested <- rolling_avg_3_tbl_nested %>% 
  mutate(fitted = data %>% map(tidy_loess))

loess_tbl_nested$fitted[[1]]

loess_tbl_nested %>% 
  unnest()
```



### Visualize Results

```{r}
loess_tbl_nested %>% 
  unnest() %>% 
  ggplot(aes(x = month_end, total_price, colour = category_2)) +
  
  # Geometries 
  geom_point() +
  geom_line(aes(y = .fitted), colour = "blue", size = 2) +
  geom_smooth(method = "loess", span = 0.2, se = FALSE) +
  facet_wrap(~category_2, scales = "free_y")
```



