---
title: "101_wk4_Adv_Vis"
author: "Seung Hyun Sung"
date: "11/10/2021"
output: html_document
---

# DS4B 101-R: R FOR BUSINESS ANALYSIS ---- 
# ADVANCED BUSINESS PLOTS ----

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(tidyverse)
library(lubridate)
library(tidyquant)

bike_orderlines_tbl <- read_rds("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```



## 1.0 Lollipop Chart: Top N Customers 

* - Great for showing order

Question: How much purchasing power is in top 5 customers?
Goal: Visualize top N customers in terms of Revenue, include cumulative percentage


```{r}
n <- 10
```

### Data Manipulation


### Data Visualization





# 2.0 Heatmaps ----
# - Great for showing details in 3 dimensions

# Question: Do specific customers have a purchasing prefernce?
# Goal: Visualize heatmap of proportion of sales by Secondary Product Category

# Data Manipulation


# Data Visualization