---
title: "101_wk_6_modeling_part1"
author: "Seung Hyun Sung"
date: "11/18/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DS4B 101-R: R FOR BUSINESS ANALYSIS 
# CUSTOMER SEGMENTATION
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(umap)
library(ggrepel)
library(tidyquant)

bike_orderlines_tbl <- read_rds("~/Desktop/University_business_science/DS4B_101/00_data/bike_sales/data_wrangled/bike_orderlines.rds")

glimpse(bike_orderlines_tbl)
```



# 1.0 CUSTOMER TRENDS ----

* Get Data in Format that trends can be compared
* - GOAL: Mine Customer Purchase History for similarity to other "like" customers
* - TECHNIQUES: K-Means Clustering, UMAP 2D Projection

# 1.1 Get Customer Trends ----

#### Part1: Aggregation 

* Aggregating purchasing trends to customer & products is typically the way to go 

* Get what are the general trends are between the products 

* must be careful on how granular the aggregation can be 

Pro tip: When understanding customer trends, it is important to collect:

* The unique customer name

* Attributes related to the product 

* A value to measure (e.g. quantity or total price)

Pro tip 2: We convert to customer trends by: 

* Aggregating within customer-product groups, then

* Normalising within customer groups to get percentages of product purchases by customer 

* need to meausre that we are aggregating on (either quantity or quality, in here quantity or total_price)

```{r}
bike_orderlines_tbl %>% 
    # trying to get the essence of what they like 
    select(bikeshop_name, price, model, category_1, category_2, frame_material, quantity) %>% 
    # summarise + group_by
    group_by(bikeshop_name, price, model, category_1, category_2, frame_material) %>% 
    summarise(quantity_purchased = sum(quantity)) %>% 
    ungroup() 
    
```
#### Part2: Normalisation

* Ultimately we want user item format 

* Normalise the data: to be compared on -> easiest way is to compute the proportions 

```{r}
customer_trends_tbl <- bike_orderlines_tbl %>% 
    # trying to get the essence of what they like 
    select(bikeshop_name, price, model, category_1, category_2, frame_material, quantity) %>% 
    # summarise + group_by
    group_by(bikeshop_name, price, model, category_1, category_2, frame_material) %>% 
    summarise(quantity_purchased = sum(quantity)) %>% 
    ungroup() %>% 
    
    # Normalisation
    group_by(bikeshop_name) %>% 
    mutate(prop_of_total = quantity_purchased/sum(quantity_purchased)) %>% 
    ungroup()

customer_trends_tbl
```

# 1.2 Convert to User-Item Format (e.g. Customer-Product) ----

```{r}
customer_product_tbl <- customer_trends_tbl %>% 
    select(bikeshop_name, model, prop_of_total) %>% 
    spread(key = model, value = prop_of_total, fill = 0)

customer_product_tbl
```




# 2.0 MODELING: K-MEANS CLUSTERING ----

# 2.1 Performing K-Means ----
kmeans(x, centers, iter.max = 10, nstart = 1,
       algorithm = c("Hartigan-Wong", "Lloyd", "Forgy",
                     "MacQueen"), trace=FALSE)

x	: numeric matrix of data, or an object that can be coerced to such a matrix (such as a __numeric vector__ or a __data frame with all numeric columns__).

K-means picks a random starting point and then iteratively finds the best location for the centers. Choosing nstart > 1 ensures higher likeihood that a good center is found. -> better acurracy. 

The kmeans function also has an nstart option that attempts multiple initial configurations and reports on the best one. For example, adding nstart = 25 will generate 25 initial configurations. This approach is often recommended.

#### The output of kmeans is a list with several bits of information. The most important being:

* cluster: A vector of integers (from 1:k) indicating the cluster to which each point is allocated.

* centers: A matrix of cluster centers.

* totss: The total sum of squares.

* withinss: Vector of within-cluster sum of squares, one component per cluster.

* tot.withinss: Total within-cluster sum of squares, i.e. sum(withinss).

* betweenss: The between-cluster sum of squares, i.e. $totss-tot.withinss$.

* size: The number of points in each cluster.

```{r}
kmeans_obj <- customer_product_tbl %>% 
    select(-bikeshop_name) %>% 
    # algorithm that performs K-means clustering in R 
    kmeans(3, nstart = 100)


kmeans_obj$cluster
```


# 2.2 Tidying a K-Means Object ----

__tot.withinss__: total Within Sum of Squares 

The metric we will use to help determine what number of clusters to use 
```{r}
kmeans_obj %>% 
    broom::tidy() 

kmeans_obj %>% 
    broom::glance()

broom::augment(kmeans_obj, customer_product_tbl) %>% 
    select(bikeshop_name, .cluster)


```


# 2.3 How many centers (customer groups) to use? ----
 

* Here goal is Scree Plot: To make it we need to calculate tot.withinss for many centers

* Iteration: can use purrr::map 

Step1: Create function that can be iterated: will make a kmeans mapper

Pro Tip: We can apply broom::glance() row-wise with mutate() + map()
```{r}
# Functions that works on 1 element 
center <- 3
kmeans_mapper <- function(centers = 3){
    customer_product_tbl %>% 
        select(-bikeshop_name) %>% 
        kmeans(centers = centers, nstart = 100)
}

3 %>% kmeans_mapper %>% glance()

# Mapping the function to many elements 
kmeans_mapped_tbl <- tibble(centers = 1:15) %>% 
    mutate(k_means = centers %>% map(kmeans_mapper),
           glance  = k_means %>% map(glance))

kmeans_mapped_tbl 
```

# 2.4 Skree Plot ----

#### unnest: we can finding the optimal __tot.withinss__

The first task is to figure out the right number of clusters. This is done with a scree plot. Essentially, the goal is to find where the curve starts to flatten significantly. Since the K-Means algorithm is effectively minimizing the differences between the centers of the clusters and each point of data, this shape of curve that starts steep then asymptotically approaches some level of a flat line is created [1]. While not a complete requirement, it is generally a good idea to scale the data when making clusters with the scale() function or another normalization technique to get more accurate results.

```{r}
kmeans_mapped_tbl %>% 
    unnest(glance) %>% 
    select(centers, tot.withinss) %>% 
    
    # Visualisation 
    ggplot(aes(centers, tot.withinss)) +
    geom_point(colour = "#2c3e50", size = 4) +
    geom_line(colour = "#2c3e50", size = 1) +
    ggrepel::geom_label_repel(aes(label = centers), colour = "#2c3e50") +
    
    # Formatting
    theme_tq() +
    labs(
        # What is the plot + the analysis on 
        title = "Skree Plot",
        # Explain what Sktree Plot does 
        subtitle = "Measures the distance each of the customer are from the classes K-Means center",
        caption ="Based on the Skree Plot its substantial decrease in variance class-within stops after 4 centers; 
        hence we select 4 clusters to segement the customer base."
    )

```


# 3.0 VISUALIZATION: UMAP ----

# 3.1 Use UMAP to get 2-D Projection ----

Once K-Means Clustering is performed, we can use UMPA to help visualise 

What UMAP does is it takes high dimensional space to 2D representation 

UMAP: A dimensionality reduction technique that captures the struture of a higgh-dimension data set (many numeric columns) in a two column (x and y) data set

# 3.2 Use K-Means to Add Cluster Assignments ----

```{r}
umap_obj <- customer_product_tbl %>% 
    select(-bikeshop_name) %>% 
    umap()

umap_result_tbl <- umap_obj$layout %>% 
    as_tibble() %>% 
    setNames(c("x", "y")) %>% 
    bind_cols(
        customer_product_tbl %>% select(bikeshop_name)
        )

umap_result_tbl %>% 
    ggplot(aes(x, y)) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = bikeshop_name), size = 3)
    
```
```{r}
umap_result_tbl

kmeans_mapped_tbl %>% 
    # When used on the k_means column, will pull the "list" of k-means objects.
    pull(k_means) %>% 
    #pluck(): allows us to extract an element from a list using an number 
    pluck(4)

# Could also done the same thing by:
kmeans_4_obj <- kmeans_mapped_tbl %>% 
    filter(centers == 4) %>% 
    pull(k_means) %>% 
    pluck(1)

kmeans_4_clusters_tbl  <- kmeans_4_obj %>% 
    augment(customer_product_tbl) %>% 
    select(bikeshop_name, .cluster)

umap_kmeans_4_results_tbl <- umap_result_tbl %>% 
    left_join(kmeans_4_clusters_tbl)
```

# 3.3 Visualize UMAP'ed Projections with Cluster Assignments ----

```{r}
umap_kmeans_4_results_tbl %>% 
    mutate(label_text = str_glue("Customer: {bikeshop_name}
                                 Cluster: {.cluster}")) %>% 
    ggplot(aes(x = x, y = y, colour = .cluster))+
    geom_point() +
    ggrepel::geom_label_repel(aes(label = label_text), size = 2) +
    # Formatting
    theme_tq() +
    scale_colour_tq() +
    labs(
        title = "Customer Segmentation: 2D Projection",
        subtitle = "UMAP 2D projection with  K-Means Cluster Assignment",
        caption = "Conclusion: 4 Customer Segemnts Identified Using K-means + UMAP Algorithms"
    ) +
    theme(legend.position = "none")
```

 
# 4.0 ANALYZE PURCHASING TRENDS ----

```{r}
customer_trends_tbl %>% 
    pull(price) %>% 
    quantile(probs = seq(0,1,1/3)) 

cluser_trend_tbl <- customer_trends_tbl %>% 
    # join cluster assigment by bikeshop name
    left_join(umap_kmeans_4_results_tbl, by = "bikeshop_name") %>% 
    mutate(price_bin = case_when(price >= quantile(price, 
                                                   probs = seq(0,1,1/3))[3] 
                                 ~ "high",
                                 price >= quantile(price, 
                                                   probs = seq(0,1,1/3))[2] 
                                 ~ "medium",
                                 TRUE ~ "low")) %>% 
    select(.cluster, model, contains("price"),
           category_1:quantity_purchased) %>% 
    # Aggregate quantity purchased by cluster and product attributes
    # group_by_at: A scoped cariant of group_by() that allows us to select columns with tidy_select helpers (e.g. contains(), col_name1:col_nameN, etc)
    group_by_at(.vars = vars(.cluster:frame_material)) %>% 
    summarise(total_quantity = sum(quantity_purchased)) %>% 
    ungroup() %>% 
    
    # Normalise data
    # Calculate proportion of total
    group_by(.cluster) %>% 
    mutate(prop_of_total = total_quantity/sum(total_quantity)) %>% 
    ungroup()
```

#### In marketing do not just show the visualisation, after identifying the clusters dive little deeper and investigate what are the preferences (top products, revenue contribution) are in each clusters.

```{r}
# Cluster 1 - Low/Medium Price, Road Model Preference
cluser_trend_tbl %>% 
    filter(.cluster == 2) %>% 
    arrange(desc(prop_of_total)) %>% 
    mutate(cum_prop = cumsum(prop_of_total)) 
```

```{r}
get_cluster_tend <- function(cluster = 1){
    cluser_trend_tbl %>% 
    filter(.cluster == cluster) %>% 
    arrange(desc(prop_of_total)) %>% 
    mutate(cum_prop = cumsum(prop_of_total)) 
}

# Cluster 1 - low/medium Price, Mountain Model, Sport Frame Material Preference
get_cluster_tend(1) 

# Cluster 3 - Medium/High Price, Mountain model, Carbon Frame Material Preference
get_cluster_tend(3) 

# Cluster 3 - High End Price, Road model, Carbon Frame Material Preference
get_cluster_tend(4) 
```

# Update Visaulisation 

```{r}
cluster_label_tbl <- tibble(
    .cluster = 1:4,
    .cluster_label = c(
        "Low/Medium Price|Mountain|Sport Frame",
        "Low/Medium Price|Road Model|Aluminum/Carbon Frame",
        "High End Price|Mountain model|Carbon Frame",
        "High End Price|Road model|Carbon Frame")) %>% 
    mutate(.cluster = as_factor(as.character(.cluster)))

umap_kmeans_4_results_tbl %>% 
    left_join(cluster_label_tbl, by = ".cluster") %>% 
    mutate(label_text = str_glue("Customer: {bikeshop_name}
                                 Cluster{.cluster}:{.cluster_label}")) %>% 
    ggplot(aes(x = x, y = y, colour = .cluster))+
    geom_point() +
    ggrepel::geom_label_repel(aes(label = label_text), size = 2) +
    # Formatting
    theme_tq() +
    scale_colour_tq() +
    labs(
        title = "Customer Segmentation: 2D Projection",
        subtitle = "UMAP 2D projection with  K-Means Cluster Assignment",
        caption = "Conclusion: 4 Customer Segemnts Identified Using K-means + UMAP Algorithms"
    ) + theme(legend.position = "none")
```

